Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-11-21 ICLR25/Paper_noProof.tex
rework

In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in.
To simplify the notations, we restrict the presentation to feed-forward, 
fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.

>>>>

In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \textcolor{blue}{\cite{crown}}.
To simplify the notations, we restrict the presentation to feed-forward, 
fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.

### 2024-11-21 ICLR25/formula.tex
fix some typos
rework

\section{Important neurons for accuracy and Utility function.}

In this section, we evaluate how each neuron would impact the accuracy of encoding this neuron with an integer (actually binary) or a linear variable. We will say we open a neuron when this neuron is selected with a binary variable. We denote by $X$ a choice of set of open neurons, and by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.

Let $z$ be a neuron of the DNN we want to evaluate, for instance computing an upper bound on the value it can take. We denote by $n < z$ the fact that a neuron $n$ appears on a layer before the layer of $z$, and $n \leq z$ if it can also be $z$.
Let us denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ 
maximizing $z$. In particular, $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.

Consider ($\Sol\_\max_\emptyset^z(n))_{n \leq z}$ (this can be obtained very efficiently by {\em one} call to an LP solver). An accurate utility function is to evaluate 
$\Improve\_\max^z(a)=$ $\Sol\_\max_\emptyset^z(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, 
representing how much opening neuron $a < z$ reduces the maximum computed for $z$
compared with using only LP. 
We have $\Improve\_\max^z(a)\geq 0$ as $\Sol\_\max_{\{a\}}^z$ fullfils all the constraints of 
$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{a\}}^z(z) \leq$ $\Sol\_\max_\emptyset^z(z)$.
Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
$\Improve\_\min^z(a)$. Calling MILP on $\mathcal{M}_{\{a\}}$ for each neuron $a \leq z$
would however be very time consuming when the number of neurons $a$ to evaluate is large.
Instead, we focus on the following upper bounding of $\Improve\_\max^z(a)$.

@@

For all neurons $n$, let $\sol(n)=$$\Sol\_\max_\emptyset^z(n)$ be the value of neuron $a$
in the solution of the LP instance $\Sol\_\max_\emptyset^z$ to maximize $z$.
%For one layer before the target layer, the formula is simple and most accurate. 
To estimate $\Improve\_\max^z(a)$, we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$, by computing by how much the value of $z$ will change if $a$ is opened
and other values remain the same - in particular, $value(\hat{a})=\ReLU(sol(a))$. We define:
%we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.

	$$\Utility\_\max\nolimits^z(a) = W_{az} \times (\sol(\hat{a})- \ReLU(\sol(a)))$$

@@

In the case $W_{az}<0$, to maximize $z$, the LP engine sets $\sol(\hat{a})$ to its minimal value, which is $\sol(\hat{a})=\ReLU(\sol(a))$ thanks to Prop.~\ref{LP}. In this case, we have $\Utility\_\max^z(a)=0$.
Thus, we have $\Utility\_\max^z(a) \geq 0$ in all cases
as $\sol(\hat{a}) \geq \ReLU(\sol(a))$ by Prop.~\ref{LP}. 
We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}. Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$. In particular, for all nodes $a$ with $W_{az}< 0$,
this node will have the smallest $\Utility\_\max\nolimits^z(a)=0$ (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$. This is one stricking difference (but not the only one) with choosing utility based on 
$|W_{az}|$ \cite{DivideAndSlide}.

@@

\medskip

Now, consider neuron a $a$ two layers before $z$. We use $b$ to denote neurons in the layer $\ell$ between $a$ and $z$. 
If we open $a$ without changing its value $\sol(a)$, then the change $\Delta(\hat{a})$ in the weight of $\hat{a}$ is 
$\Delta(\hat{a})=\ReLU(\sol(a)) - \sol(\hat{a}) \leq 0$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through $\ell$. 
We let $\Delta(b) = W_{ab}\Delta(\hat{a})$ for all $b \in \ell$.
Based on Proposition \ref{LP}, we can evaluate the impact 
$\Delta(\hat{b})$ of opening $a$ on the value of each $\hat{b}$, by using the upper and lower bound $\UB(b),\LB(b)$:

@@

$$ \Utility\_\max\nolimits^z(a) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})$$

	\begin{proof}
    Consider $\sol'(n))_{n \leq z})$ with
	$\sol'(n)=\sol(n)$ for all $n \notin \{z,\hat{a}\} \cup \{b,\hat{b} \mid b \in \ell\}$. In particular,  $\sol'(a) = \sol(a)$.
	Now, define $\sol'(\hat{a}) = \ReLU(\sol(a))$. 
	That is, $\sol'(\hat{a})$ is the correct value for $\hat{a}$, obtained if we open neuron $a$, compared to the LP abstraction for $\sol(\hat{a})$.
	We also define $\sol'(b)=\sol(b)+\Delta(b)$ and 
	$\sol'(\hat{b})=\sol(\hat{b}) + \Delta(\hat{b})$.
	Last, $\sol'(z)=\sol(z) + \sum_{b \in \ell} W_{bz} \Delta(\hat{b})$.
	% = \sol(z) - \Utility\_\max\nolimits^z(a)$.

	It is easy to check that $(\sol'(n))_{n \leq z}$ satisfies the constraints in 
	$\mathcal{M}_{\{a\}}$, as opening $a$ changes the value of $\hat{a}$ from
	$\sol(\hat{a})$ to $\ReLU(\sol(a))$, and the contribution from $a$ to $b,\hat{b},z$ 
	are respected.
	As $\sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $\sol'(z) \leq$ $\Sol\_\max_{\{a\}}^z(z)$. That is, 
	$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
	$ \Utility\_\max^z(a) \geq \Improve\_\max^z(a)$.
	In particular, we have that $\Utility\_\max^z(a) \geq 0$, which was not obvious from the definition.
	\end{proof}

>>>>

\section{Utility function choosing neurons important for accuracy.}

\label{sec4}

In this section, we evaluate how each neuron would impact the accuracy of encoding this neuron with a binary or a linear variable, using Proposition \ref{LP}. A neuron is {\em open} when it is represented as a binary variable. For $X$ a set of open neurons, we denote by $\mathcal{M}_X$ the MILP model where variables from $X$ are encoded with binary variables, and other variables are using the LP linear relaxation.

Assume that we want to compute an upper bound for neuron $z$ on layer $\ell_z$.
We write $n < z$ if neuron {\color{blue} $n$ is} on a layer before $\ell_z$, and $n \leq z$ if $n< z$ or $n=z$. We denote ($\Sol\_\max_X^z(n))_{n \leq z}$ a solution of $\mathcal{M}_X$ maximizing $z$. In particular, $\Sol\_\max_X^z(z)$ is the maximum of $z$ under $\mathcal{M}_X$.

Consider $(sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
%(this can be obtained very efficiently by {\em one} call to an LP solver).
Function
$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
compared with using only LP. 
We have $\Improve\_\max^z(n)\geq 0$ as $\Sol\_\max_{\{n\}}^z$ fulfills all the constraints of 
$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{n\}}^z(z) \leq \sol(z)$.
Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
$\Improve\_\min^z(n)$. Calling MILP on $\mathcal{M}_{\{n\}}$ for each neuron $n \leq z$
would however be very time consuming when the number of neurons $a$ to evaluate is large.
{\color{blue} 
That's why as far as we know, in competing heuristics to rank important nodes (e.g. \cite{huang2017safety,crown}), no call to solvers are made.
%Instead, we focus on the following $\Utility\_\max\nolimits^z(n)$ function upper bounding $\Improve\_\max^z(n)$. 
The novelty of our Utility function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, which is very efficient and negligible wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes, as hinted by Proposition \ref{prop2}.

@@

%For all neurons $n$, let $\sol(n)=$$\Sol\_\max_\emptyset^z(n)$ be the value of neuron $a$
%in the solution of the LP instance $\Sol\_\max_\emptyset^z$ to maximize $z$.
%For one layer before the target layer, the formula is simple and most accurate. 
%To estimate $\Improve\_\max^z(a)$,

For a neuron $b$ on the layer before the layer $\ell_z$, we define:

%we define $\Utility\_\max^z(a)$, first for neurons $a$ one layer before $z$, by computing by how much the value of $z$ will change if $a$ is opened
%and other values remain the same - in particular, $value(\hat{a})=\ReLU(sol(a))$. We define:
%we first need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.
\vspace{-0.4cm}
	$$\Utility\_\max\nolimits^z(b) = W_{bz} \times (\sol(\hat{b})- \ReLU(\sol(b)))$$
\vspace{-0.4cm}

@@

Notice that if $W_{bz}<0$, the LP engine sets $\sol(\hat{b})$ to its minimal value
to maximize $z$, which is $\sol(\hat{b})=\ReLU(\sol(b))$ thanks to Proposition~\ref{LP}. 
In this case, we have $\Utility\_\max^z(b)=0$.
Thus, we have $\Utility\_\max^z(b) \geq 0$ in all cases
as $\sol(\hat{b}) \geq \ReLU(\sol(b))$ by Proposition~\ref{LP}.

For a neuron a $a$ two layers before $\ell_z$, 
$b$ denoting neurons in the layer $\ell$ just before $\ell_z$, 
we define:

\begin{align*}
	\Delta(\hat{a}) &= \ReLU(\sol(a))-\sol(\hat{a})\\
	\forall b \in \ell, \Delta(b) &= W_{ab}\Delta(\hat{a})\\
	\forall b \in \ell, \Delta(\hat{b}) &=
	\begin{cases}
		\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} > 0\\
		\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)\geq0\\
		\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} < 0 \text{ and } \sol(b)<0		 
	\end{cases}\\
	\Utility\_\max\nolimits^z(a) &= -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})
\end{align*}

%We will show with a more general definition that $0 \leq \Improve\_\max^z(a) \leq \Utility\_\max^z(a)$ in Prop.~\ref{prop2}.

Informally, $\Delta(\hat{a}), \Delta(b), \Delta(\hat{b})$ approximate the improvement on the accuracy of $\hat{a}, b, \hat{b}$ when computing $\ReLU(a)$ 
using the exact MILP encoding instead of LP. Using Prop. \ref{LP}, we show:

Thus, $\Utility\_\max^z(a)$ can be used to approximate $\Improve\_\max^z(a)$. 
In particular, for all nodes $a$ with $W_{az}< 0$,
this node will have the smallest $\Utility\_\max\nolimits^z(a)=0$ (thus will not get picked in the open nodes $X$), and indeed it is not having any impact on  $\Sol\_\max_{\{a\}}^z(z)$. This is one striking difference (but not the only one) with choosing utility based on 
$|W_{az}|$ \cite{DivideAndSlide}.

@@

	\begin{proof}
    Consider $\sol'(n)_{n \leq z}$ with
	$\sol'(n)=\sol(n)$ for all $n \notin \{z,\hat{a}\} \cup \{b,\hat{b} \mid b \in \ell\}$. In particular,  $\sol'(a) = \sol(a)$.
	Now, define $\sol'(\hat{a}) = \ReLU(\sol(a))$. 
	That is, $\sol'(\hat{a})$ is the correct value for $\hat{a}$, obtained if we open neuron $a$, compared to the LP abstraction for $\sol(\hat{a})$.
	We define $\sol'(b)=\sol(b)+\Delta(b)$ and 
	$\sol'(\hat{b})=\sol(\hat{b}) + \Delta(\hat{b})$.
	Last, $\sol'(z)=\sol(z) + \sum_{b \in \ell} W_{bz} \Delta(\hat{b})$.
	We will show:
	\begin{equation}
		\label{eq12}
		(\sol'(n))_{n \leq z} \text{ satisfies the constraints in } \mathcal{M}_{\{a\}}
	\end{equation} 
	This suffices to conclude: as
	$\sol'(z)$ is a solution of $\mathcal{M}_{\{a\}}$, it is smaller or equal to the maximal solution: $\sol'(z) \leq$ $\Sol\_\max_{\{a\}}^z(z)$. That is, 
	$\sol(z)-\sol'(z) \geq \sol(z) -$ $\Sol\_\max_{\{a\}}^z(z)$, i.e. 
	$ \Utility\_\max^z(a) \geq \Improve\_\max^z(a)$.
	In particular, we have that $\Utility\_\max^z(a) \geq 0$, which was not obvious from the definition.

	Finally, we show (\ref{eq12}). First, opening $a$ changes the value of $\hat{a}$ from
	$\sol(\hat{a})$ to $\ReLU(\sol(a)) = sol(\hat{a}) + \Delta(a)$, 
	and from $sol(b)$ to $sol(b) + \Delta(b)$.
	The case of $\Delta(\hat{b})$ is the most interesting:
	If $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)} +$ Cst to maximize $z$.
Changing $b$ by $\Delta(b)$ thus results in changing $\sol(\hat{b})$ by 
$\frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b)$.
If $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
If $\sol(b) < 0$, then we have $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ change the 0 value only if $\sol(b)+\Delta(b)>0$. If $\sol(b) > 0$, then 
$\sol(\hat{b})=\ReLU(\sol(b))=\sol(b)$, and the change to $\hat{b}$ will be 
the full $\Delta(b)$, unless $\Delta(b) < -\sol(b) < 0$ in which case it is 
$-\sol(b)$.
		\end{proof}
	}

	\iffalse

	If we open $a$ without changing its value $\sol(a)$, then the change $\Delta(\hat{a})$ in the weight of $\hat{a}$ is 
$\Delta(\hat{a})=\ReLU(\sol(a)) - \sol(\hat{a}) \leq 0$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through $\ell$. 
We let $\Delta(b) = W_{ab}\Delta(\hat{a})$ for all $b \in \ell$.
Based on Proposition \ref{LP}, we can evaluate the impact 
$\Delta(\hat{b})$ of opening $a$ on the value of each $\hat{b}$, by using the upper and lower bound $\UB(b),\LB(b)$:

@@

$$ \Utility\_\max\nolimits^z(a) = -\sum_{b \in \ell} W_{bz} \Delta(\hat{b})$$
\fi

### 2024-11-21 ICLR25/introduction.tex
rework

Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-Crown \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neighbour with a different decision. One issue is however that easy instances are trained specifically to be easier to verify
e.g. using DiffAI \cite{DiffAI} PGD \cite{PGD}, which can impact the accuracy of the network, i.e. answering correctly to an unperturbed input. For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct (the other $71\%$ are thus not even tested by $\alpha,\beta$-Crown). While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g. very hard verification instances into hard verification instances.
Also, verification questions intrinsically harder than local robustness, such as 
bounding on Lipschitz constants \cite{lipshitz} globally or asking several specification at once, makes the instance particularly harder. Last, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks \cite{SDPFI}. 
The bottom line is, one cannot expect only {\em easy} verification instances: {\em hard} verification instances need to be explored as well.

>>>>

Easy instances does not mean small DNNs: for instance, a ResNet architecture for CIFAR10 (with tens of thousands of neurons) has been fully checked by $\alpha,\beta$-Crown \cite{crown}, each instance taking only a couple of seconds to either certify that there is no robustness attack, or finding a very close neighbour with a different decision. One issue is however that easy instances are trained specifically to be easier to verify
e.g. using DiffAI \cite{DiffAI} PGD \cite{PGD}, which can impact the accuracy of the network, i.e. answering correctly to an unperturbed input. For instance, this ResNet was trained using Wong, and only $29\%$ of its answers are correct {\color{blue}\cite{prima}} (the other $71\%$ are thus not  tested). While more accurate trainers for verification have been recently developed \cite{TrainingforVerification}, they can only simplify one given verification specification by a limited amount before hurting accuracy, turning e.g. very hard verification instances into hard verification instances.
Also, verification questions intrinsically harder than local robustness, such as 
bounding on Lipschitz constants \cite{lipshitz} globally or asking several specification at once, makes the instance particularly harder. Last, there are many situations (workflow, no access to the dataset...) where using specific trainers to learn easy to verify DNN is simply not possible, leading to  {\em verification-agnostic} networks \cite{SDPFI}. 
The bottom line is, one cannot expect only {\em easy} verification instances: {\em hard} verification instances need to be explored as well.

### 2024-11-21 ICLR25/valabstraction.tex
rework

Consider the simpler abstraction, termed ``Box abstraction" \cite{deeppoly}: it inductively computes the bounds for each neuron in the subsequent layer independently. This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth. 
For all $i \geq 3$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
Taking the DNN example from Fig \ref{fig1}, assume $x_1,x_2 \in [-1,1]$. This implies that $x_3,x_4 \in [-2,2]$. After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to $[0,2]$, leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$. 
The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val_{\vy}(n_i)=\alpha$. However, this precision is lost from the next layer (beginning with $n_5, n_6$) due to potential dependencies among preceding neurons. For example, it is impossible for $x_5=\Val_{\vx}(n_5)$ to reach $6$, as it would necessitate both $x_3=2$ and $x_4=2$, which is not possible at the same time as 
$x_3=2$ implies $x_1=x_2=1$ and $x_4=2$ implies $x_2=-1$ (and $x_1=1$), a contradiction.

@@

$$\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\UB(n) \cdot (1-a)$$

@@

The crucial factor in such an approach is to {\em select} few opened neurons in $X$ which are the most important for the accuracy. An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$. To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP abstraction.

Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$. 
Let $x$ represent the input value of $n$, hence with 
$\LB(n) < x < \UB(n)$, and $\hat{x}$ representing $\ReLU(x)$. 
We have:

\begin{proposition}
	\label{LP}
	The LP relaxation on $\hat{x}$ is equivalent with:
	\begin{align}
		\ReLU(x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} \label{eq:deeppoly}
	\end{align} 
\end{proposition}

\begin{proof}
The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediatly equivalent with $\hat{x} \geq \ReLU(x)$.

@@

Notice that this is close to the DeepPoly abstractions \cite{deeppoly}, but LP simultaneous considers the two linear lower bounding functions for the ReLU operation, namely $\ReLU(x) \geq 0$ and $\ReLU(x) \geq x$, while the DeepPoly abstraction restricts itself to the application of a single one of these linear bounding functions.

>>>>

Consider the simpler abstraction, termed ``Box abstraction", {\color{blue} recalled e.g. in \cite{deeppoly}}: it inductively computes the bounds for each neuron in the subsequent layer independently. This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth. 
For all $i \geq 3$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
Taking the DNN example from Fig \ref{fig1}, assume $x_1,x_2 \in [-1,1]$. This implies that $x_3,x_4 \in [-2,2]$. After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to $[0,2]$, leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$. 
The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val_{\vy}(n_i)=\alpha$. However, this precision is lost from the next layer (beginning with $n_5, n_6$) due to potential dependencies among preceding neurons. For example, it is impossible for $x_5=\Val_{\vx}(n_5)$ to reach $6$, as it would necessitate both $x_3=2$ and $x_4=2$, which is not possible at the same time as 
$x_3=2$ implies $x_1=x_2=1$ and $x_4=2$ implies $x_2=-1$ (and $x_1=1$), a contradiction.

{\color{blue} In \cite{DBLP_Ehlers17, deeppoly} and others, the {\em triangular abstraction} was proposed:
\begin{align}
	\ReLU(x) = max (0,x) \leq \hat{x} \leq \UB(n) \frac{x-\LB(n)}{\UB(n)-\LB(n)} 
	\label{eq:deeppoly}
\end{align} 
It has two lower bounds (the 0 and identity functions), and one upper bound. 
DeepPoly \cite{deeppoly} chooses one of the two lower bounds for each neuron $x$, giving rise to a greedy quadratic-time algorithm to compute very fast an abstraction of the value of $\hat{x}$ (but not that accurately).
}

@@

\vspace{-0.4cm}
\begin{equation}\quad \hat{x} \geq x \quad \wedge \quad \hat{x} \geq 0, \quad \wedge \quad \hat{x} \leq \LB(n) \cdot a \quad \wedge \quad \hat{x} \leq x-\UB(n) \cdot (1-a)
\label{eq11}
\end{equation}

@@

The crucial factor in such an approach is to {\em select} few opened neurons in $X$ which are the most important for the accuracy. An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$. To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP relaxation of (\ref{eq11}). We obtain:

%Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$. 
%Let $x$ represent the input value of $n$, hence with 
%$\LB(n) < x < \UB(n)$, and $\hat{x}$ representing $\ReLU(x)$. 
%We have:

\begin{proposition}
	\label{LP}
	{\color{blue} The LP relaxation of (\ref{eq11}) is equivalent with the triangular abstraction 	(\ref{eq:deeppoly}).}
\end{proposition}

{\color{blue}
To the best of our knowledge, we could not find such an equivalence stated in the bibliography, although the proof is simple. This result will be instrumental for our Utility function (Section \ref{sec4}).}

\begin{proof}
	Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$.
The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediatly equivalent with $\hat{x} \geq \ReLU(x)$.

@@
